### 2021-09-14 sections/healthcare_application/main.tex
Include payoff matrices

>>>>

Matrices \(A\) and \(B\) represent the original payoff matrices while matrices
\(\tilde{A}\) and \(\tilde{B}\) represent the incentivised payoff matrices.
It can be observed that matrix \(\tilde{A}\) is a scaled version of matrix 
\(A\) only on the row that is most frequently played and similarly matrix 
\(\tilde{B}\) of matrix \(B\) only on the column that is most frequently played
(see figure \ref{fig:ard_penalty}).

\tiny
\begin{equation*}
    A = 
    \begin{bmatrix}
        0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 \\
        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845 & 0.9995466 & 0.999539 \\
        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874 & 0.9996734 & 0.999649  \\
        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832 & 0.9998909 & 0.9998517 \\
        0.99999996 & 0.99999994 & 0.99999992 & 0.99999988 & 0.99999973 & 0.9999989 & 0.9999859 \\
        0.9998773 & 0.99987995 & 0.99988236 & 0.99988643 & 0.99989417 & 0.9999126 & 0.9999712
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    B = 
    \begin{bmatrix}
        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942 &  1.0 & 0.99982128 \\
        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153 & 0.99999997 & 0.9998333  \\
        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286 & 0.99999966 & 0.99985269 \\
        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667 & 0.99999921 & 0.99986701 \\
        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077 & 0.9999972 & 0.9998958  \\
        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407 & 0.99997106 & 0.99997276 \\
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    \tilde{A} = 
    \begin{bmatrix}
        0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 \\
        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845 & 0.99954656 & 0.99953879 \\
        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874 & 0.99967339 & 0.9996492  \\
        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832 & 0.9998909 & 0.99985171 \\
        0.99969996 & 0.99969994 & 0.99969992 & 0.99969988 & 0.99969973 & 0.99969895 & 0.99968586 \\
        0.9998773 &  0.99987995 & 0.99988236 & 0.99988643 & 0.99989417 & 0.99991264 & 0.99997122
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    \tilde{B} = 
    \begin{bmatrix}
        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942 &  0.9997 & 0.99982128 \\
        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153 & 0.99969997 & 0.9998333 \\
        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286 & 0.99969966 & 0.99985269 \\
        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667 & 0.99969921 & 0.99986701 \\
        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077 & 0.9996972 & 0.9998958 \\
        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407 & 0.99967106 & 0.99997276
    \end{bmatrix}
\end{equation*}
\normalsize
